An improved metric for the analysis of swarms

### 2018-01-03 paper.tex
Time Added

@@

\begin{table}[H]
\begin{center}
\begin{tabular}{| l | l | l | l | l | l |}
\hline
Log &	Id &	N.Id &	Distance &	{\color{green}Cohesion} &	{\color{red}Repulsion} 	\\ \hline
7 & 76 &	91 & 55.39031 & {\color{green}276.95156} & {\color{red}276.94684} \\ \hline
24 & 75 & 6 & 55.39032 & {\color{green}276.95160} & {\color{red}276.94661} \\ \hline
32 & 72 & 38 &	55.39002603773678 & {\color{green}276.95013} & {\color{red}276.95370} \\ \hline
35 &	63 & 64 & 55.39022 &	{\color{green}276.95113} &	{\color{red}276.94887} \\
\hline
\end{tabular}\caption{Data extract ($|k_cv_c| \approx |k_rv_r|$)} \label{tab:SampleEquilibrium}
\end{center}
\end{table}

@@

\section{Distance based metric\label{section:DistanceDynamics}}
The distance-based metric considers a swarm in terms of how the agents are physically distributed: i.e. only the inter-agent distances and their standard deviation are considered. The standard deviation indicates the extent to which the swarm is out of balance and will move to re-balance itself. If the standard deviation is zero then all the agents are evenly spaced.

@@

\section{Calculating distance based internal movement}
Equation~\ref{eq:SwarmStabilityDistance1} computes the means distance of an agent to its neighbours $nbr(b)$. 
%% The relative position vector generated for an agent $b$ to its neighbour $b'$, $bb'$, is shown in~(\ref{eq:FlyToCentre1}). The magnitude of that vector gives the distance between two agents. For an individual agent the average magnitude $\mu_d(b)$ is calculated as \ref{eq:SwarmStabilityDistance1} where $b$ is the agent and $|nbr(b)|$ is the number of neighbours.

@@

\section{Cohesion/repulsion internal movement model}\label{Section:StabilityModel}
Section~ref{Section:StabilityMagnitude}~discussed calculation of resultant cohesion~(Equation \ref{eq:FlyToCentre1}) and resultant repulsion~(Equation \ref{eq:Repulsion1}) vectors for each agent deriving a combined \emph{cohesion/repulsion vector} via equation~\ref{eq:InterAgentMovement2}.

@@

Now, we define for each agent $b$ a scalar, $P(b)$, a measure of the extent to which the neighbours of $b$ are cohering inwards or repelling outwards this is Equation~\ref{eq:CohesionRepulsion}.

\begin{equation}
\label{eq:CohesionRepulsion}
P(b) = \left\{\begin{array}{lll}
               |M(b)|& if & |k_cv_c(b)| > |k_r v_r(b)|\\
              -|M(b)|& otherwise
              \end{array}\right.
\end{equation}

Although it is possible for agent $b$ to have a resultant vector of null there could still be a variation in the constituent components. The variation calculation (standard deviation) is shown in~\ref{Section:VarianceInPotential}. \ref{eq:SwarmStabilityMetricT} is the mean of the \emph{agent resultant magnitudes} for an agent and its neighbours where $|nbr(b)|$ is the number of neighbours.

\begin{equation}
\label{eq:SwarmStabilityMetricT}
\mu_p(b) = \frac{P(b)}{|nbr(b)|}
\end{equation}

@@

To identify the swarm based \emph{agent resultant magnitude}~Equation~\ref{eq:SwarmStabilityMetricT} must be extended to iterate over all the agents in the swarm. \ref{eq:SwarmStabilityMetricT3} shows $\mu_p(S)$~as the swarm based magnitude.

@@

\section{Standard deviation in agent cohesion/repulsion metric}\label{Section:VarianceInPotential}
To improve the metric clarification in terms of the deviation from the \emph{cohesion/repulsion metric} norm is calculated. The standard deviation of the entire swarm  is shown in Equation \ref{eq:SwarmStabilityMetricT}.

The standard deviation is calculated as Equation~\ref{eq:SwarmStabilityQuotientT} where $\sigma_p(S)$ is the standard deviation at a time $t$ and $\mu_p(S)$ is the mean at the same point in time.

@@

The metric for the internal movement is a set of numbers, the mean and standard deviation of the swarm's internal \emph{agent resultant magnitude} derived from each agent and its neighbour interactions~(Equation~\ref{eq:SwarmPotentialMagnitude}). The pair $\mu_p(S)$, $\sigma_p(S)$ may be written informally as:

\begin{equation}
\label{eq:SwarmPotentialMagnitude}
\psi_p = \mu_p(S)\pm \sigma_p(S)
\end{equation}

>>>>

\section{Modelling movement}\label{sec:Movement1}
Each agent within a swarm calculates its \textit{movement-direction vector} based on its \textit{interaction} and \textit{destination} vectors. The \textit{movement vector}~($b_{pos}$) is calculated using the unit \textit{movement-direction vector} of Equation~\ref{eq:InterAgentMovement2} multiplied by the time elapsed~($t$) in the system and the speed characteristic of the agent~($s_b$).

This process is carried out for every agent in the swarm to genrate the swarm's next position.

\begin{center}
\begin{equation}
\label{eq:AgentMovement}
b_{pos}=s_{b}t\big(v(b)\big)\string^ 
\end{equation}‎
\end{center}

The increment in the location of agent $b$ over time interval $t$ is shown in Equation~\ref{eq:AgentMovement} where $s_b$ is the speed of agent~$b$.

@@

\begin{table}[H]
\begin{center}
\begin{tabular}{| l | l | l | l | l | l |}
\hline
Log &	Id &	N.Id &	Distance &	{\color{green}Cohesion} &	{\color{red}Repulsion} 	\\ \hline
7 & 76 &	91 & 55.39031 & {\color{green}276.95156} & {\color{red}276.94684} \\ \hline
24 & 75 & 6 & 55.39032 & {\color{green}276.95160} & {\color{red}276.94661} \\ \hline
32 & 72 & 38 &	55.39002 & {\color{green}276.95013} & {\color{red}276.95370} \\ \hline
35 & 63 & 64 & 55.39022 &	{\color{green}276.95113} &	{\color{red}276.94887} \\
\hline
\end{tabular}\caption{Data extract ($|k_cv_c| \approx |k_rv_r|$)} \label{tab:SampleEquilibrium}
\end{center}
\end{table}

@@

\section{Distance metric\label{section:DistanceDynamics}}
The distance metric considers a swarm in terms of how the agents are physically distributed: i.e. only the inter-agent distances and their standard deviation are considered. The standard deviation indicates the extent to which the swarm is out of balance and will move to re-balance itself. If the standard deviation is zero then all the agents are evenly spaced.

@@

\section{Calculating distance internal movement}
Equation~\ref{eq:SwarmStabilityDistance1} computes the means distance of an agent to its neighbours $nbr(b)$. 
%% The relative position vector generated for an agent $b$ to its neighbour $b'$, $bb'$, is shown in~(\ref{eq:FlyToCentre1}). The magnitude of that vector gives the distance between two agents. For an individual agent the average magnitude $\mu_d(b)$ is calculated as \ref{eq:SwarmStabilityDistance1} where $b$ is the agent and $|nbr(b)|$ is the number of neighbours.

@@

\section{Cohesion/repulsion internal movement model}\label{Section:StabilityModel}
Section~\ref{Section:StabilityMagnitude}~discussed calculation of resultant cohesion~(Equation \ref{eq:FlyToCentre1}) and resultant repulsion~(Equation \ref{eq:Repulsion1}) vectors for each agent deriving a combined \emph{cohesion/repulsion vector} via equation~\ref{eq:InterAgentMovement2}.

@@

Now, we define for each agent $b$ a \emph{cohesion/repulsion scalar}, $P(b)$, to measure the influence of the neighbours of $b$ on $b$ as cohesive (positive) or repulsive (negative); this is Equation~\ref{eq:CohesionRepulsion}.

\begin{equation}
\label{eq:CohesionRepulsion}
P(b) = \left\{\begin{array}{lll}
               |v(b)|& if & |k_cv_c(b)| > |k_r v_r(b)|\\
              -|v(b)|& otherwise
              \end{array}\right.
\end{equation}

Although it is possible for $v(b)$ to be null there could still be variation in the constituent components. The variation calculation (standard deviation) is shown below.

%% Equation~\ref{eq:SwarmStabilityMetricT} is the mean of the cohesion/repulsion scalar for an agent.
%% 
%% \begin{equation}
%% \label{eq:SwarmStabilityMetricT}
%% \mu_p(b) = \frac{P(b)}{|nbr(b)|}
%% \end{equation}

@@

The mean cohesion/repulsion scalar for the swarm is now given by~Equation~\ref{eq:SwarmStabilityMetricT3}.

@@

%% \section{Standard deviation in agent cohesion/repulsion metric}\label{Section:VarianceInPotential}
%% To improve the metric clarification in terms of the deviation from the \emph{cohesion/repulsion metric} norm is calculated. The standard deviation of the entire swarm  is shown in Equation \ref{eq:SwarmStabilityMetricT}.

The standard deviation associated with this mean is calculated as Equation~\ref{eq:SwarmStabilityQuotientT}.
%%  where $\sigma_p(S)$ is the standard deviation and $\mu_p(S)$ is the mean at the same point in time.

@@

The metric for the internal movement is this pair of numbers, the mean and standard deviation of the swarm's internal \emph{cohesion/repulsion}. The pair $\mu_p(S)$, $\sigma_p(S)$ may be written informally as:

\begin{equation}
\label{eq:SwarmPotentialMagnitude}
\psi_p(S) = \mu_p(S)\pm \sigma_p(S)
\end{equation}

Figure~\ref{coord:BaselineMagnitude1} shows the evolution of the metric in time.
